Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-06-17 final/cleanpaper/pedestrian_forecasting_iros_2017.tex
Revision with Citation.
More modifications.

%%% first author
\author{Henry O. Jacobs, Owen K. Hughes, Matthew Johnson-Roberson, and Ram Vasudevan
 \thanks{ H.O. Jacobs, O. Hughes, M. Johnson-Roberson, and R.~Vasudevan are with the University of Michigan, Ann Arbor, MI 48109
{\scriptsize \{\texttt{hojacobs,owhughes,mattjr,ramv}\}~\texttt{@umich.edu}}}
\thanks{This material is based upon work supported by Ford Motor Company and the National Science Foundation under Grant No. 1562612.}
}

@@

\section{Efficient Probability Propagation} \label{sec:efficient}
%As mentioned, many of the modeling choices are born out of a balance between accuracy and real-time computability.
%One of the major modeling choices, that agents move approximately according to a small number of ODEs, is the most prominent such choice.
This section details how the modeling of the agent's motion as satisfying an ODE can be leveraged to compute $\rho_t(x_t)$ quickly and accurately.
To begin, rather than focusing on computing $\rho_t(x_t)$, we describe how to compute the joint probability $\Pr( x_t , \hat{x}_0, \hat{v}_0)$.
We can obtain $\rho_t(x_t)$ by normalizing $\Pr( x_t , \hat{x}_0, \hat{v}_0)$ with respect to integration over $x_t$.
We can approximate the integration over $s$ in \eqref{eq:decomposition}, with a Riemann sum.
Due to space limitations, the proofs of all the results presented in this section can be found in \cite{}.

@@

The output distributions of the four algorithms were compared using their integrals over the cells of a regular grid over our domain. 
These integrals are used to visualize the distributions in Figures \ref{fig:bookstore-1-2} and \ref{fig:death-1-2}.
%In keeping with our measurement model, the ground truth compared against was a grid that was identically zero except on a bounding box around the measurement at time $t$. 
%The ground truth bounding box at each time instance were set equal to the average bounding box dimension centered at the 
%were the average bounding box dimensions in the training data set. 
Because our predictions all share the same scale, we amalgamate all of the prediction and truth values for all of the simulated agents at a given time step and generate ROC curves.
In our analysis, we sought a metric that evaluated the utility of prediction algorithms in the autonomous vehicle context. 
	In this instance it is critical that the generated set of predictions contains the ground-truth observed trajectory while including as few false positive detections as possible.
	ROC curves which plot the true positive rate against the false positive rate evaluate this aforementioned safety criteria for autonomous vehicles exactly. 
	To generate the true positive rate and false positive rate, a probability distribution has to be thresholded to yield a binary map. 
	Each chosen threshold creates a point on the ROC curve. 
	% We treat every value of each bounding box as a threshold.
	The Area Under the Curve (AUC) is a standard measure of the quality of a predictor.  
	The closer that this AUC is to one, the better the prediction algorithm. 
	%Each method of generating thresholds creates a different AUC, ours in particular corresponds to the AUC variant from \cite{Judd2009}. 
	Figure \ref{fig:auc_vs_time} illustrates the AUC of each algorithm versus time.

>>>>

%%% first author
\author{Henry O. Jacobs, Owen K. Hughes, Matthew Johnson-Roberson, and Ram Vasudevan
 \thanks{ H.O. Jacobs, O.K. Hughes, M. Johnson-Roberson, and R.~Vasudevan are with the University of Michigan, Ann Arbor, MI 48109
{\scriptsize \{\texttt{hojacobs,owhughes,mattjr,ramv}\}~\texttt{@umich.edu}}}
\thanks{This material is based upon work supported by Ford Motor Company and the National Science Foundation under Grant No. 1562612.}
}

@@

\section{Efficient Probability Propagation} \label{sec:efficient}
%As mentioned, many of the modeling choices are born out of a balance between accuracy and real-time computability.
%One of the major modeling choices, that agents move approximately according to a small number of ODEs, is the most prominent such choice.
This section details how the modeling of the agent's motion as satisfying an ODE can be leveraged to compute $\rho_t(x_t)$ quickly and accurately.
To begin, rather than focusing on computing $\rho_t(x_t)$, we describe how to compute the joint probability $\Pr( x_t , \hat{x}_0, \hat{v}_0)$.
We can obtain $\rho_t(x_t)$ by normalizing $\Pr( x_t , \hat{x}_0, \hat{v}_0)$ with respect to integration over $x_t$.
We can approximate the integration over $s$ in \eqref{eq:decomposition}, with a Riemann sum.
Due to space limitations, the proofs of all the results presented in this section can be found in \cite{Jacobs2017}.

@@

The output distributions of the four algorithms were compared using their integrals over the cells of a regular grid over our domain. 
These integrals are used to visualize the distributions in Figures \ref{fig:bookstore-1-2} and \ref{fig:death-1-2}.
%In keeping with our measurement model, the ground truth compared against was a grid that was identically zero except on a bounding box around the measurement at time $t$. 
%The ground truth bounding box at each time instance were set equal to the average bounding box dimension centered at the 
%were the average bounding box dimensions in the training data set. 
Because our predictions all share the same scale, we amalgamate all of the prediction and truth values for all of the simulated agents at a given time step and generate ROC curves.
In our analysis, we sought a metric that evaluated the utility of prediction algorithms in the autonomous vehicle context. 
	In this instance it is critical that the generated set of predictions contains the ground-truth observed trajectory while including as few false positive detections as possible.
	ROC curves which plot the true positive rate against the false positive rate evaluate this aforementioned safety criteria for autonomous vehicles exactly. 
	To generate the true positive rate and false positive rate, a probability distribution has to be thresholded to yield a binary map. 
	Each chosen threshold creates a point on the ROC curve. 
	%We treat every value of each bounding box as a threshold.
	The Area Under the Curve (AUC) is a standard measure of the quality of a predictor \cite{Judd2009}.  
	The closer that this AUC is to one, the better the prediction algorithm .
	%Each method of generating thresholds creates a different AUC, ours in particular corresponds to the AUC variant from \cite{Judd2009}. 
	Figure \ref{fig:auc_vs_time} illustrates the AUC of each algorithm versus time.
